### 2020-02-08 appendix.tex
appendix

\subsection{Reproducing results on hundreds of models}

>>>>

\subsection{Reproducing the CV and NLP models }

We provide a github repository for this paper that includes jupyter notsbooks that fully reproduce all results.
All results have been produced using the weightwatcher tool (v0.2.7).
The ImageNet and OpenAI GPT pretrained models are provided in the current pyTorch, torchvision, and huggingface distributions,
as specified in the \texttt{requirements.txt} file.
The ImageNet-1K models, and other models in section 6), are taken from the \textttr{omsr/imgclsmob}
``Sandbox for training convolutional networks for computer vision'' github repository.

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|}
\hline
Figure & Notebook \\
\hline
1  &  WeightWatcher-VGG.ipynb \\
2(a)  &  WeightWatcher-ResNet.ipynb \\
2(b)  &  WeightWatcher-ResNet-1K.ipynb \\
3(a)  &  WeightWatcher-VGG.ipynb \\
3(b)  &  WeightWatcher-ResNet.ipynb \\
3(c)  &  WeightWatcher-DenseNet.ipynb \\
\hline
5 & WeightWatcher-OpenAI-GPT2.ipynb \\
6, 7 & WeightWatcher-OpenAI-GPT2.ipynb \\
\hline
\end{tabular}
\end{center}
\caption{Jupyter notesbooks used to reproduce sections 4 and 5}
\label{table:notebooks}
\end{table}

\subsection{Reproducing Section 6}
